Article Title

### 2013-12-27 plos.tex
minor

In our study, we focused on estimating a specific parameter of the distribution (its covariance matrix) rather than fitting a specific parametric distribution.  Under the loss function (Eq.~\ref{eq:loss}) we selected, the covariance matrix estimation methods are equivalent to fitting a multivariate Gaussian model and selecting the best structure on the basis of cross-validated log-likelihood. However, the ranking of models was preserved under other loss functions (Fig.~S\ref{fig:supp02}), indicating that model selection results were not strongly dependent on the assumption of gaussianity. We defend the practice of evaluating and optimizing probabilistic models with respect to their parameters that are more relevant for functional connectivity rather than maximizing their cross-validated log likelihoods, which are sensitive to all parameters. For example, model A may attain higher cross-validated log likelihood than model B due to its better ability to capture the tails of the distribution while model B better estimates the correlation matrix. We maintained that model B must be more relevant for studies of functional connectivity because correlations do reflect aspects of functional connectivity.

@@

Orientation tuning was computed by fitting the mean firing rates in response to gratings of directions $\phi$ with two-peaked von Mises tuning functions of the form $f(\phi)=a + b\exp\left[(\cos(\phi-\theta)-1)/w\right] + c\exp\left[(-\cos(\phi-\theta)-1)/w\right]$ where $b\ge c$ are amplitudes of the two respective peaks, $w$ is the tuning width, and  $\theta$ is the preferred direction. The significance of the fit was determined by the permutation test: the labels of the direction were randomly permuted 10,000 times.  The $p$-value of the fit was computed as the fraction of permuted datasets for which the $R^2$ value of the tuning function fit exceeded that of the real data.  Cells were considered tuned for $p$-values not exceeding $0.05$.

>>>>

In our study, we focused on estimating a specific parameter of the distribution (its covariance matrix) rather than fitting a specific parametric distribution.  Under the loss function (Eq.~\ref{eq:loss}) we selected, the covariance matrix estimation methods are equivalent to fitting a multivariate Gaussian model and selecting the best structure on the basis of cross-validated log-likelihood. However, the ranking of models was preserved under other loss functions (Fig.~S\ref{supp:02}), indicating that model selection results were not strongly dependent on the assumption of gaussianity. We defend the practice of evaluating and optimizing probabilistic models with respect to their parameters that are more relevant for functional connectivity rather than maximizing their cross-validated log likelihoods, which are sensitive to all parameters. For example, model A may attain higher cross-validated log likelihood than model B due to its better ability to capture the tails of the distribution while model B better estimates the correlation matrix. We maintained that model B must be more relevant for studies of functional connectivity because correlations do reflect aspects of functional connectivity.

@@

Orientation tuning was computed by fitting the mean firing rates in response to gratings of directions $\phi$ with two-peaked von Mises tuning functions of the form $f(\phi)=a + b\exp\left[\frac 1 w(\cos(\phi-\theta)-1) \right] + c\exp\left[\frac 1 w(\cos(\phi-\theta+\pi)-1) \right]$ where $b\ge c$ are amplitudes of the two respective peaks, $w$ is the tuning width, and  $\theta$ is the preferred direction. The significance of the fit was determined by the permutation test: the labels of the direction were randomly permuted 10,000 times.  The $p$-value of the fit was computed as the fraction of permuted datasets for which the $R^2$ value of the tuning function fit exceeded that of the real data.  Cells were considered tuned for $p$-values not exceeding $0.05$.
